Reparametrization of COM-Poisson Regression Models with Applications in the Analysis of Experimental Count Data

### 2018-10-30 presentations/2018mca/slides-mca2018.Rnw
Improve the directory names

\title[Reparametrization of COM-Poisson Regression Models]{
  Reparametrization of COM-Poisson Regression Models for Analysis of
  Count Data}

\author[Eduardo E. Ribeiro Jr]{
  Eduardo Elias Ribeiro Junior \inst{1} \inst{2} \\
  Walmes Marques Zeviani \inst{1} \\
  Wagner Hugo Bonat \inst{1} \\
  Clarice Garcia Borges Demétrio \inst{2} \\
  John Hinde \inst{3}
}

@@

\begin{frame}{Orthogonality property of the MLEs}
\vspace{-0.3cm}

@@

\begin{frame}{Soybean data}
\vspace{-0.2cm}
<<desc-soy, fig.width=9, fig.height=5.8, fig.cap="">>=

knitr::include_graphics("figure/desc-soy-1")

@@

library(latticeExtra)
source("../../codes/lattice-panels.R")

benchs <- readRDS("../../codes/comparetimes.rds")
xlabs <- expression("COM-Poisson", "COM-Poisson"[mu])
bwplot(time ~ expr | case,
       ylab = "Time (seconds)",
       scales = list(
           y = list(relation = "free"),
           x = list(at = 1:2, labels = xlabs)
       ),
       data = benchs)

@@

\section*{Bibliography}
\begin{frame}[allowframebreaks]{References}
  \small
  \vspace*{-0.5cm}
  \bibliography{../../references.bib}
\end{frame}

>>>>

\title[Reparametrization of COM-Poisson Regression Models]{
  Reparametrization of COM-Poisson Regression Models with Applications
  in the Analysis of Experimental Count Data}

\author[Clarice Garcia Borges Demétrio]{
  Eduardo Elias Ribeiro Junior \inst{1} \inst{2} \\
  Walmes Marques Zeviani \inst{1} \\
  Wagner Hugo Bonat \inst{1} \\
  Clarice Garcia Borges Demétrio \inst{2} \\
  John Hinde \inst{3}
}

@@

\begin{frame}{Orthogonality property of the MLEs}

@@

@@

library(latticeExtra)
source("../codes/lattice-panels.R")

benchs <- readRDS("../codes/comparetimes.rds")
xlabs <- expression("COM-Poisson", "COM-Poisson"[mu])
bwplot(time ~ expr | case,
       ylab = "Time (seconds)",
       scales = list(
           y = list(relation = "free"),
           x = list(at = 1:2, labels = xlabs)
       ),
       data = benchs)

@@

\section*{Bibliography}
\begin{frame}[allowframebreaks]{References}
  \small
  \vspace*{-0.5cm}
  \bibliography{../references.bib}
\end{frame}
